EDIpack2: interoperable Lanczos-based solver for generic quantum impurity problems

### 2025-05-11 03_edipack2.tex
Minor change in Quantum Numbers modes (essentially a test to sync OF with Gihub)

 - The {\bf normal} case conserves both the total occupation $N$
and the total magnetization $S_z$, or equivalently, the total number
of electrons with spin up $N_\up$ and down $N_\dw$.
Optionally, the symmetry
can be extended to act indipendently to each orbital and spin
component, i.e., $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
specific case is discussed extensively
Ref.~[\onlinecite{Amaricci2022}] and will not be further covered here.

@@

- The {\bf superc} case maintains onlu the $S_z$ conservation,
allowing the total charge to not be conserved. This setting captures
system with $s$-wave superconductivity, including 
intra- and inter-orbital pairing.

- The {\bf nonsu2} case conserves the total
charge $N$ while allowing spin symmetry group to be not conserved.
This scenario catpures effects such as local spin-orbit coupling
$\vec{L}\cdot\vec{S}$~\cite{something}, in-plane spin ordering~\cite{BellomiaKMH} or
in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.

>>>>

\begin{itemize}
\item{} The {\bf normal} case conserves both the total occupation $N$
and the total magnetization $S_z$, or equivalently, the total number
of electrons with spin up $N_\up$ and down $N_\dw$.
Optionally, the symmetry
can be extended to act indipendently to each orbital and spin
component, i.e., $\vec{N_\s}=[N^1_\s,\dots,N^{N_\a}_\s]$. This
specific case is discussed extensively
Ref.~[\onlinecite{Amaricci2022}] and will not be further covered here.

@@

\item{} The {\bf superc} case maintains onlu the $S_z$ conservation,
allowing the total charge to not be conserved. This setting captures
system with $s$-wave superconductivity, including 
intra- and inter-orbital pairing.

\item{} The {\bf nonsu2} case conserves the total
charge $N$ while allowing spin symmetry group to be not conserved.
This scenario catpures effects such as local spin-orbit coupling
$\vec{L}\cdot\vec{S}$~\cite{something}, in-plane spin ordering~\cite{BellomiaKMH} or
in-plane spin-triplet exciton condensation~\cite{Amaricci2023_excitons,Blason}.  
\end{itemize}
